### 2017-03-23 appendix.tex
adding the review directory
towards main result

\begin{appendix}
\textbf{On choice of $\N$:}\\
It is desirable to get rid of the assumption that $\tr\in \N$ without affecting our arguments. Note that the set $\N$ is not used in ALP \eqref{alp} and the feasible set of ALP can be specified as the set $\S\eqdef\{r\in \R^k| \Phi r \geq T\Phi r\}$. Further, the only property about $\S$ that we used in our argument (\Cref{restate}) was that $r'= r^*+\norm{J^*-\Phi r^*}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \S$. Thus, so long as $\N$ contains $r'$ it is not necessary for it to contain $\tr$.\par
Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \R^k}{\arg\min}\norm{J^*-\Phi r}_{\mn}$. Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $\norm{J^*-\Phi r^*}_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $\norm{J^*-\Phi r^*}_{\mn}\leq \norm{J^*-\Phi r^*}_{\infty}$).  The fact that $r'\in \N$ can then be ensured when $\N\eqdef\{\r| a\leq \Phi r\leq b\}$, where $a=\frac{g_{\min}}{1-\alpha}$ and $b=\frac{g_{\max}}{1-\alpha}+\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\frac{g_{\max}-g_{\min}}{1-\alpha}$.
\end{appendix}

>>>>

\begin{appendix}
\textbf{On choice of $\N$:}
It is desirable to get rid of the assumption that $\tr\in \N$ without affecting our arguments. Note that the set $\N$ is not used in ALP \eqref{alp} and the feasible set of ALP can be specified as the set $\S\eqdef\{r\in \Re^k| \Phi r \geq T\Phi r\}$. Further, the only property about $\S$ that we used in our argument (\Cref{restate}) was that $r'= r^*+\norm{J^*-\Phi r^*}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \S$. Thus, so long as $\N$ contains $r'$ it is not necessary for it to contain $\tr$.\par
Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \Re^k}{\arg\min}\norm{J^*-\Phi r}_{\mn}$. Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $\norm{J^*-\Phi r^*}_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $\norm{J^*-\Phi r^*}_{\mn}\leq \norm{J^*-\Phi r^*}_{\infty}$).  The fact that $r'\in \N$ can then be ensured when $\N\eqdef\{\r| a\leq \Phi r\leq b\}$, where $a=\frac{g_{\min}}{1-\alpha}$ and $b=\frac{g_{\max}}{1-\alpha}+\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\frac{g_{\max}-g_{\min}}{1-\alpha}$.
\end{appendix}

### 2017-03-23 errana.tex
adding the review directory
towards main result

%!TEX root =  autocontgrlp.tex
\section{Error Analysis}\label{sec:improv}
\subsection{Properties of the Bellman Operator}
We now state without proof the most important properties of the Bellman operator(s).
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
\begin{comment}
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\end{comment}
\begin{lemma}\label{tprop} The following hold:
\begin{enumerate}[(i)]
\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
\item \label{shift}
Given $J\in \R^n$ and $t \in \R$, we have $T(J+t\one)=TJ+\alpha t\one$.
\item \label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
$
\norm{TJ_1-TJ_2}_\infty\leq \alpha \norm{J_1-J_2}_\infty.
$
\item \label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{enumerate}
\end{lemma}
\begin{corollary}
If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.\par
We now present the analysis to derive the improved bounds where the idea is to show that the novel projection operators ($\Gamma/\hg$) are contraction maps. To this end, we go through steps similar to \Cref{tprop}-\eqref{monotone},~\eqref{shift} and ~\eqref{maxnorm}. Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
\subsection{Analysis using Lyapunov Functions}
\begin{definition}\label{def:lyap}
Let $c,\rho,\chi:S \to \R_+$ be positive-valued functions. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
The function $\chi:S\to\R_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$.
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\item \label{wassmp} $W \in \R^{nd\times m}_+$ is a matrix with all positive entries.
\end{enumerate}
\end{assumption}
The authors of \cite{ALP} express the error bounds in terms of $\frac{1}{1-\beta_{\psi}}$.  A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability. Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov functions based analysis to obtain error bounds that exploit the structure of the underlying MDP. In particular, the prior bounds suggests that ALP is likely to generate good approximations when the underlying MDP is stable. We also adopt a similar approach by stating our results using Lyapunov function based arguments.

We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,

@@

Let $A\in \R^{u\times v}$, $b\in \R^u,d\in \R^v$ and $b_0=Ax_0$ for
some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then

@@

Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,

@@

For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.

@@

Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$. Choose any $i\in \{1, \ldots, n\}$. Since $J_1\leq J_2$, from \Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, the result follows.

@@

Assume that $\hg: \R^n \to \R^n$ is monotone and 
that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,

@@

First, we show that for any $t\ge 0$,  $J\in \R^n$,

@@

Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.

@@

%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.

@@

The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.

@@

The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.

@@

and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.

@@

and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 

@@

$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:

@@

$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:

@@

\min_{r\in \R^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb

@@

\begin{align}\label{jhv}

@@

For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$.

@@

For  $r \in \R^k$ arbitrary, let $r'$ be

@@

%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 

>>>>

%!TEX root =  autocontgrlp.tex
\section{Error Analysis}\label{sec:improv}
\subsection{Properties of the Bellman Operator}
We now state without proof the most important properties of the Bellman operator(s).
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
\begin{comment}
First, we introduce some extra notation:
For $J_1,J_2\in \Re^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \Re^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\end{comment}
\begin{lemma}\label{tprop} The following hold:
\begin{enumerate}[(i)]
\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \Re^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
\item \label{shift}
Given $J\in \Re^n$ and $t \in \Re$, we have $T(J+t\one)=TJ+\alpha t\one$.
\item \label{maxnorm}
If $T: \Re^n \to \Re^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \Re^n$,
$
\norm{TJ_1-TJ_2}_\infty\leq \alpha \norm{J_1-J_2}_\infty.
$
\item \label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{enumerate}
\end{lemma}
\begin{corollary}
If $J\in \Re^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.\par
We now present the analysis to derive the improved bounds where the idea is to show that the novel projection operators ($\Gamma/\hg$) are contraction maps. To this end, we go through steps similar to \Cref{tprop}-\eqref{monotone},~\eqref{shift} and ~\eqref{maxnorm}. Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
\subsection{Analysis using Lyapunov Functions}
\begin{definition}\label{def:lyap}
Let $c,\rho,\chi:S \to \Re_+$ be positive-valued functions. Then for $J\in \Re^n$, $a\in A$ and $s\in S$, define
the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
The function $\chi:S\to\Re_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \Re^n$.
\item \label{lyap} $\psi\colon S \ra \Re_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \Re^k$, $\Phi r_0 = \psi$.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \Re$, where $r_0\in \Re^k$ such that $\Phi r_0 = \psi$.
\item \label{wassmp} $W \in \Re^{nd\times m}_+$ is a matrix with all positive entries.
\end{enumerate}
\end{assumption}
The authors of \cite{ALP} express the error bounds in terms of $\frac{1}{1-\beta_{\psi}}$.  A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability. Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov functions based analysis to obtain error bounds that exploit the structure of the underlying MDP. In particular, the prior bounds suggests that ALP is likely to generate good approximations when the underlying MDP is stable. We also adopt a similar approach by stating our results using Lyapunov function based arguments.

We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \Re^n$ and $t>0$,

@@

Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
some $x_0 \in \Re^v$, $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. Then

@@

Let $r^*\eqdef\underset{r\in \Re^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,

@@

For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.

@@

Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$. Choose any $i\in \{1, \ldots, n\}$. Since $J_1\leq J_2$, from \Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, the result follows.

@@

Assume that $\hg: \Re^n \to \Re^n$ is monotone and 
that there exists some $\beta\in [0,1)$ such that for any $J\in \Re^n$ and $t>0$,

@@

First, we show that for any $t\ge 0$,  $J\in \Re^n$,

@@

Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.

@@

%For any $J\in \Re^n$, $t\in \Re_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.

@@

The operator $\Gamma  \colon \Re^n\ra \Re^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.

@@

The operator $\hg:\Re^n\to\Re^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.

@@

and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.

@@

and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 

@@

$\hat{r} \in \Re^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:

@@

$\tr \in \Re^k$ is a solution to ALP \eqref{alp} iff it solves the following program:

@@

\min_{r\in \Re^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb

@@

\begin{align*}%\label{jhv}

@@

For this result, recall that $r_0 \in \Re^k$ is the vector such that $\psi = \Phi r_0$.

@@

For  $r \in \Re^k$ arbitrary, let $r'$ be

@@

%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \Re^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \Re^n$. 
